\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-18 latex/article_vol2.tex

%% an abstract and keywords
\Abstract{Data cleaning and -validation are the first steps in any data
  analysis, as the validity of the conclusions from the analysis are
  hinged on the quality of the input data. Mistakes in the data can arise for any number of reasons, including erroneous codings, malfunctioning measurement equipment, inconsistent data generation manuals and many more.  Ideally, a human investigator
  should go through each variable in the dataset and look for
  potential errors --- both in input values and coding.  \hl{segway: But, ...}

  We describe an \proglang{R} package which implements an extensive
  and customizeable suite of quality assessment tools to be applied to
  a dataset in order to identify potential problems in its variables. The results can be presented in an auto-generated, non-technical, stand-alone
  overview document, intended to be perused by an investigator with an
  understanding of the variables in the data and the experimental design, but not necessarily knowledge of \R{R}. Thereby, \R{cleanR} aids the dialogue between data analysist and field experts, while also providing easy documentation of data cleaning steps and data quality control. Moreover, the \R{cleanR} solution changes the data cleaning process from the usual ad hoc approach to a systematic, well-documented endeavor. 
  \R{cleanR} also provides a suite of more typical \R{R} tools for interactive data quality assessment and -cleaning.

  The \pkg{cleanR} package is designed to be easily extended with custom
  user-created checks that are relevant in particular situations. \hl{Already said that above. Either expand on it or delete this.}
}
\Keywords{data cleaning, quality control, \proglang{R}}
\Plainkeywords{data cleaning, quality control, R} %% without formatting
%% at least one keyword must be supplied

@@

\section{Introduction}
Though data cleaning might be regarded as a somewhat dull activity, adequate data cleaning is crucial in any data analysis. With ever-growing dataset sizes and complexities, statisticians and data analysts find themselves spending a large portion of their time on
data cleaning and on data wrangling. \proglang{R}-packages such as
\pkg{data.table}, and \pkg{plyr} have made data wrangling a lot easier, but there are only a few tools available for data cleaning. \hl{What are these tools? More here about the solutions already available.}

>>>>

%% an abstract and keywords
\Abstract{Data cleaning and -validation are the first steps in any
  data analysis, as the validity of the conclusions from the analysis
  hinges on the quality of the input data. Mistakes in the data can
  arise for any number of reasons, including erroneous codings,
  malfunctioning measurement equipment, inconsistent data generation
  manuals and many more.  Ideally, a human investigator should go
  through each variable in the dataset and look for potential errors
  --- both in input values and coding --- but that process can be very
  time-consuming, expensive and error-prone by itself.

  We describe an \proglang{R} package which implements an extensive
  and customizeable suite of quality assessment tools to be applied to
  a dataset in order to identify potential problems in its
  variables. The results can be presented in an auto-generated,
  non-technical, stand-alone overview document, intended to be perused
  by an investigator with an understanding of the variables in the
  data and the experimental design, but not necessarily knowledge of
  \R{R}. Thereby, \R{cleanR} aids the dialogue between data analysist
  and field experts, while also providing easy documentation of data
  cleaning steps and data quality control. Moreover, the \R{cleanR}
  solution changes the data cleaning process from the usual ad hoc
  approach to a systematic, well-documented endeavor.  \R{cleanR} also
  provides a suite of more typical \R{R} tools for interactive data
  quality assessment and -cleaning. \hl{Hvad menes der/henvises der
    til  med denne sætning?}

  % The \pkg{cleanR} package is designed to be easily extended with
  % custom user-created checks that are relevant in particular
  % situations. \hl{Already said that above. Either expand on it or
  % delete this.}
}
\Keywords{data cleaning, quality control, \proglang{R}}
\Plainkeywords{data cleaning, quality control, R} %% without formatting
%% at least one keyword must be supplied

@@

\section{Introduction}
Though data cleaning might be regarded as a somewhat tedious activity,
adequate data cleaning is crucial in any data analysis. With
ever-growing dataset sizes and complexities, statisticians and data
analysts find themselves spending a large portion of their time on
data cleaning and on data wrangling. \proglang{R}-packages such as
\pkg{data.table}, and \pkg{plyr} have made data wrangling a lot
easier, but there are only a few tools available for data
cleaning. \hl{What are these tools? More here about the solutions
  already available.}
